Interval Probability for Fuzzy Quantum Theories

### 2016-06-30 prob.tex
prob.tex \subsection{Quantum Probability Measures} Fix a typo...
prob.lyx Find a bug...>"<

@@

Another difference between classical and quantum probabiltiy space. For a
given set of events $\events$, there are many possible probability measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007},
a postulate of quantum mechanics, states that each pure normalized
($\ip{\phi}{\phi}=1$) quantum state $\ket{\phi}$ induces a probability measure
$\mu^B_{\phi}$ as follows: 
\[
\mu^B_{\phi}(P)=\ip{\phi}{P\phi}
\]

>>>>

Although specifying a probability for every event looks complex, a
probability measure can be simply constructed by $\pmeas(E)=\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in E}}\rho(\omega)$,
where $\rho:\Omega\rightarrow[0,1]$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in\Omega}}\rho(\omega)=1$.
Furthermore, every probability measure~$\pmeas$ can be written in
this form for an unique $\rho$~\cite{Kolmogorov1950,Swart2013}
which is called the probability distribution~\cite{GrahamKnuthPatashnik1994}.

@@

Another difference between classical and quantum probability space. For a
given set of events $\events$, there are many possible probability measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007},
a postulate of quantum mechanics, states that each pure normalized
($\ip{\phi}{\phi}=1$) quantum state $\ket{\phi}$ induces a probability measure
$\mu^B_{\phi}$ as follows: 
\[
\mu^B_{\phi}(P)=\ip{\phi}{P\phi}
\]
